Windowed residual-minimization model reduction for dynamical systems

### 2019-10-02 main.tex
up

This work seeks to overcome the practical challenges associated with existing
residual minimization approaches for reduced-order models. To this end, we
propose the \methodName\ method for model reduction, which minimizes the FOM ODE residual
over a sequence of time windows. The key novelties of the work are two fold.
First, the residual minimization problem is formulated to minimize the
\textit{time-continuous} residual. By working from a time-continuous viewpoint, the
present formulation decouples the underlying temporal discretization scheme
from the residual minimization problem; thus addressing a key deficiency of
LSPG \KTC{This is also true for ST-LSPG and maybe other discretization-based
methods? Have to check}. The time-continuous viewpoint additionally exposes
two different methods that
can be used to solve the residual-minimization problems, namely
a \textit{discretize-then-optimize} (i.e., direct) method and
an \textit{optimize-then-discretize} (i.e., indirect) method. The second novelty
is that the residual is minimized over \textit{time windows} rather than over
a single time step or the entire time domain. This equips the method with
additionaly flexibility that enables it
to explore more fine-grained tradeoffs in computational cost and error. We
demonstrate that this method can be viewed as a generalization of existing
methods, as particular instances of this formulation recover Galerkin, LSPG,
and space--time LSPG projection. Figure~\ref{fig:flowchart} depicts how the
proposed method is related to existing approaches.

>>>>

This work seeks to overcome the practical challenges associated with existing
residual minimization approaches for reduced-order models. To this end, we
propose the \methodNameLower\ (\methodAcronym) method for model reduction,
which minimizes the FOM ODE residual over a sequence of arbitrarily defined
time windows. The key novelties of the work are twofold.  First, the method
minimizes the \textit{time-continuous}  residual (i.e., that associated with
the full-order model ODE). By adopting a time-continuous viewpoint, the
formulation decouples the underlying temporal discretization scheme from the
residual minimization problem, thus addressing a key deficiency of LSPG
\KTC{This is also true for ST-LSPG and maybe other discretization-based
methods? Have to check}. Time-continuous residual minimization also exposes
two different solution methods,  namely a \textit{discretize-then-optimize}
(i.e., direct) method and an \textit{optimize-then-discretize} (i.e.,
indirect) method. The second novelty is that the method sequentially minimizes
the residual over arbitrarily defined \textit{time windows} rather than
sequentially minimizing the residual over time steps or over the entire time
domain. This equips the method with additionaly flexibility that enables it to
explore more fine-grained tradeoffs between computational cost and error. We
demonstrate that this method can be viewed as a generalization of existing
methods, because particular instances of this formulation are equivalent to
Galerkin, LSPG, and space--time LSPG projection. Figure~\ref{fig:flowchart}
depicts how the proposed \methodAcronym\ method is related to existing
approaches.
